Remark on the hypothetical judgment

### 2015-08-01 paper.tex
...

The uniform explanation of hypothetical judgment also deprives Martin-L\"of's
framework of a propositional connective as strong as proper intuitionistic
implication. Contra Martin-L\"of's statement in the Siena lectures, the
interpretation of hypothetical judgment as material consequence is also crucial
for the semantics of his type theory, as noted by Dybjer \cite{dybjer:testing}.

>>>>

Contra Martin-L\"of's explanation in the Siena lectures, the interpretation of
hypothetical judgment as material consequence is crucial for the semantics of
his type theory, as noted by Dybjer \cite{dybjer:testing}.
